QPLIB: A Library of Quadratic Programming Instances

### 2017-02-02 format.tex
fix typos
- put back the word "integer" to make clear that type must be changed in *I*

\item [{[2]}]
For problems of type \texttt{**N} or \texttt{**B}, these lines/sections
are omitted.
\item [{[3]}]
For problems of type \texttt{L**}, this section is omitted.
\item [{[4]}]
For problems of type \texttt{**N}, \texttt{**B} or \texttt{**L},
this section is omitted.
\item [{[5]}]
For problems of type \texttt{*C*}, \texttt{*B*} or \texttt{*I*},
this section is omitted. For problems of \texttt{*I*}, binary variables
should be specified with lower and upper bounds 0 and 1.
\item [{[6]}]
For problems of type \texttt{*B*}, this section is omitted.
%Bounds for binary variables must not be specified in this section.
\end{description}
Binary variables defined either implicitly via the type \texttt{*B*}
or explicitly in the variable type section will be assumed to
have lower and upper bounds 0 and 1, and this will override any
explicit bounds $l_d$, $u_d$ $l_i$ and $u_i$ set in the lower and upper
bound sections.
To fix a binary variable to 0 or 1, its variable type should be changed
to continuous or general integer and the corresponding lower and upper
bounds set accordingly in the lower and upper bound sections.

>>>>

\item [{[2]}]
For problems of type \texttt{**N} or \texttt{**B}, these lines/sections
are omitted.
\item [{[3]}]
For problems of type \texttt{L**}, this section is omitted.
\item [{[4]}]
For problems of type \texttt{**N}, \texttt{**B} or \texttt{**L},
this section is omitted.
\item [{[5]}]
For problems of type \texttt{*C*}, \texttt{*B*} or \texttt{*I*},
this section is omitted. For problems of type \texttt{*I*}, binary variables
should be specified as integer variables with lower and upper bounds 0 and 1.
\item [{[6]}]
For problems of type \texttt{*B*}, this section is omitted.
%Bounds for binary variables must not be specified in this section.
\end{description}
Binary variables defined either implicitly via the type \texttt{*B*}
or explicitly in the variable type section will be assumed to
have lower and upper bounds 0 and 1, and this will override any
explicit bounds $l_d$, $u_d$, $l_i$, and $u_i$ set in the lower and upper
bound sections.
To fix a binary variable to 0 or 1, its variable type should be changed
to continuous or general integer and the corresponding lower and upper
bounds set accordingly in the lower and upper bound sections.
